pSEOBNRv4HM

### 2020-10-12 papers/intro_paper/intro_paper.tex
updated paper
a bit more text for the waveform model

Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies. \abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{cotesta}})This allows access to the full SNR of the signal, reducing measurement uncertainties. Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions. While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with black holes spins in the current paper. All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties.
\par
The rest of this paper is organized as follows. Section~\ref{sec:model} describes our parametrised IMR waveform model. In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies in a Bayesian formalism. Then in section~\ref{sec:results}, we demonstrate our method on real gravitational wave events, as well as simulated signals. Finally we provide a summary of our results and discuss future developments in section  The rest of this paper is organized as follows. Section~\ref{sec:model} describes our waveform model, which is then used to perform our test of black hole ringdown using Bayesian framwork, outlined in section~\ref{sec:discussion}.

\section{Waveform Model}\label{sec:model}

\abhi{Summary of the section:}

\begin{itemize}
\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
\end{itemize}

\section{Method/Bayesian PE}\label{sec:method}

>>>>

Unlike methods that focus on the post-merger signal, it describes a framework in which a complete inspiral-merger-ringdown (IMR) waveform model is used to measure the complex QNM frequencies. \abhi{It is a spinning multipolar effective-one-body waveform calibrated to numerical relativity simulations (SEOBNRv4HM~\citep{Cotesta:2018fcv}})This allows access to the full SNR of the signal, reducing measurement uncertainties. Moreover, the definition of the ringdown start time is built into the model and does not need to be either left as an additional free parameter or fixed using alternate definitions. While \paperone presented the method in the context of a non-spinning waveform model, we extend the analysis to the case with black holes spins in the current paper. All astrophysical black holes are expected to be spinning, and ignoring effects of spin have been shown to introduce systematic biases in the measurement of the source properties.
\par
The rest of this paper is organized as follows. Section~\ref{sec:model} describes our parametrised IMR waveform model. In section~\ref{sec:method}, we define our testing GR framework in which we use that model to measure the complex QNM frequencies in a Bayesian formalism. Then in section~\ref{sec:results}, we demonstrate our method on real gravitational wave events, as well as simulated signals. Finally we provide a summary of our results and discuss future developments in section  The rest of this paper is organized as follows. Section~\ref{sec:model} describes our waveform model, which is then used to perform our test of black hole ringdown using Bayesian framwork, outlined in section~\ref{sec:discussion}.

\section{Method}
\subsection{Waveform Model}\label{sec:model}

%\abhi{Summary of the section:}

%\begin{itemize}
%\item{a description of the SEOBNRv4HM model and it's generalisation to form the pSEOBNRv4HM model}
%\item{highlight the importance of spins in the model, especially with regards to the non-spinning method outlined in Brito et al.}
%\end{itemize}

As in \paperone, we use an IMR waveform model developed within the EOB formalism. However, in this work we extend the results of \paperone by using a waveform model for spinning, nonprecessing binary BHs. Namely we use as our baseline model the multipolar waveform developed in Ref.~\citep{Cotesta:2018fcv}. In addition to being calibrated to NR simulations, this model also uses information from BH perturbation theory for the merger and ringdown phases. Therefore this waveform model provides a very accurate and faithful semi-analytic description of the inspiral, merger and ringdown phases. Henceforth we will denote this model by SEOBNR for short.

In the observer's frame, the GW polarizations can be written as 
$h_+(\iota,\varphi;t ) - i h_\times(\iota,\varphi;t) = \sum_{\ell, m} {}_{-\!2}Y_{\ell m}(\iota,\varphi)\, h_{\ell m}(t)$, where $\iota$ denotes the inclination angle computed with respect to the direction perpendicular to the orbital plane, $\varphi$ is the azimuthal direction to the observer, ${}_{-\!2}Y_{\ell m}(\theta,\phi)$ are the $-2$ spin-weighted spherical harmonics. The SEOBNR model we employ includes the $(\ell, |m|)=(2,2),(2,1)$, $(3,3)$, $(4,4)$, and $(5,5)$ modes. For each $(\ell, m)$, the inspiral-(plunge-)merger-ringdown SEOBNR waveform is schematically given by $h_{\ell m}(t) = h_{\ell m}^\mathrm{insp-plunge}\, \theta(t_\mathrm{match}^{\ell m} - t) + h_{\ell m}^\mathrm{merger-RD}\,\theta(t-t_\mathrm{
    match}^{\ell m})$, where $\theta(t)$ is the Heaviside step function, $h_{\ell m}^\mathrm{insp-plunge}$ represents the inspiral-plunge part of the waveform, whereas $h_{\ell m}^\mathrm{merger-RD}$ denotes the merger-ringdown phase. 
  %  
The merger-ringdown SEOBNR modes read~\citep{Bohe:2016gbl,Cotesta:2018fcv}
%
\begin{equation}
  \label{RD}
  h_{\ell m}^\mathrm{merger-RD}(t) = \nu A_{\ell m}(t) e^{i\phi_{\ell m} (t)}\,
  e^{-i\sigma_{\ell m0} (t-t_\mathrm{match}^{\ell m})} \quad t \geq t_{\rm match}^{\ell m}\,,
\end{equation}
%
where $\nu$ is the symmetric mass ratio of the binary and $\sigma_{\ell m0} = \omega_{\ell m 0} -i/\tau_{\ell m 0}$ denotes the complex frequency of the fundamental QNMs of the remnant BH. We denote the oscillation frequencies by $\omega_{\ell m  0}\equiv \Re(\sigma_{\ell m0})$ and the decay times by $\tau_{\ell m 0}\equiv -1/\Im(\sigma_{\ell m0})$. The explicit expressions for the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ can be found in Ref.~\citep{Cotesta:2018fcv}, and are chosen such that the functions $A_{\ell  m}$ and $\phi_{\ell  m}$ are of class $C^1$ at $t=  t_{\rm match}^{\ell m}$, when matching the merger-ringdown waveform to the inspiral-plunge SEOBNR waveform $h_{\ell m}^\mathrm{inspiral-plunge}(t)$.

In the SEOBNR model constructed in Ref.~\cite{Cotesta:2018fcv}, the complex frequencies $\sigma_{\ell m 0}$  are expressed in terms of the final BH mass and spin~\cite{Berti:2005ys,Berti:2009kk}, and the latter are related to the BBH's component masses and spins through NR--fitting-formulas obtained in GR~\cite{Taracchini:2013rva,Hofmann:2016yih}. Here instead, in the spirit of what was done in \paperone, we promote the QNM (complex) frequencies to be free parameters of the model, while keeping the inspiral-plunge modes $h_{\ell m}^\mathrm{inspiral-plunge}(t)$ fixed to their GR values (henceforth, pSEOBNR model). We note that when leaving $\sigma_{\ell m}$ to vary freely, the amplitudes $A_{\ell m}(t)$ and phases $\phi_{\ell m} (t)$ will in general also differ from the GR prediction, since those functions depend on the QNM complex frequencies (see~\citep{Cotesta:2018fcv}).

For the specific applications of this paper, we will normally only allow either $\sigma_{220}$ or $\sigma_{330}$ to vary, while keeping all the other modes to coincide with GR. However the model can be easily used to measure any QNM complex frequency available in the waveform.

\subsection{Bayesian PE}\label{sec:method}
